### 2024-07-23 Tables/MD_noMD_readmort_decomp_synth.tex
Updates from Overleaf
update objects

\caption{\label{tab:MD_noMD_readmort_decomp_synth}Decomposition of Readmissions and Mortality Synthetic DiD Results}
\centering
\begin{tabular}[t]{lcccc}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{2}{c}{Weighted Avg. Readmission Rate} & \multicolumn{2}{c}{Weighted Avg. Mortality Rate} \\
 & (1) & (2) & (1) & (2)\\
\midrule
Ever MD Exec x Post Programs & 0 &  & -0.06 & \\
 & (0.06) &  & (0.06) & \\
2012 MD Exec x Post Programs &  & -0.19$^{*}$ &  & -0.1\\
 &  & (0.09) &  & (0.08)\\
 &  &  &  & \\
\addlinespace
\textbf{Comparison Group:} &  &  &  & \\
Never MD & $\checkmark$ &  & $\checkmark$ & \\
Has MD not in 2012 &  & $\checkmark$ &  & $\checkmark$\\
 &  &  &  & \\
Observations & 3925 & 1845 & 3910 & 1840\\
\bottomrule
\multicolumn{5}{l}{\textsuperscript{} Results from Equation with readmission and mortality rates as}\\
\multicolumn{5}{l}{outcome variables.}\\
\multicolumn{5}{l}{\textsuperscript{} Standard errors are clustered at the hospital level.}\\
\multicolumn{5}{l}{\textsuperscript{} Signif. codes: 0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1}\\
\end{tabular}
\end{table}

>>>>

\caption{\label{tab:MD_noMD_readmort_decomp_synth}Decomposition of Readmissions and Mortality Synthetic DiD Results}
\centering
\begin{tabular}[t]{lcccc}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{2}{c}{Weighted Avg. Readmission Rate} & \multicolumn{2}{c}{Weighted Avg. Mortality Rate} \\
 & (1) & (2) & (1) & (2)\\
\midrule
Ever MD Exec x Post Programs & -0.01 &  & 0.03 & \\
 & (0.07) &  & (0.06) & \\
2012 MD Exec x Post Programs &  & 0.17 &  & 0.12\\
 &  & (0.1) &  & (0.09)\\
 &  &  &  & \\
\addlinespace
\textbf{Comparison Group:} &  &  &  & \\
Never MD & $\checkmark$ &  & $\checkmark$ & \\
Has MD not in 2012 &  & $\checkmark$ &  & $\checkmark$\\
 &  &  &  & \\
Observations & 3005 & 1595 & 3005 & 1595\\
\bottomrule
\multicolumn{5}{l}{\textsuperscript{} Results from Equation with readmission and mortality rates as}\\
\multicolumn{5}{l}{outcome variables.}\\
\multicolumn{5}{l}{\textsuperscript{} Standard errors are clustered at the hospital level.}\\
\multicolumn{5}{l}{\textsuperscript{} Signif. codes: 0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1}\\
\end{tabular}
\end{table}
